---
title: "Content Admin"
date: "`r Sys.time()`"
output: html_document
---

This purpose of this script is to programatically manage the deployed content on Rstudio Connect.

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(rsconnect)
library(connectapi)

# Establish a connection to RStudio connect.
client <- connect(
  server = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
)

tags <- get_tags(client)$`Projects and Presentations`$`Bike Predict`
repo_url <- "https://github.com/sol-eng/bike_predict"
```


## 1 ETL

### 1.1 Raw Data Refresh

```{r}
guid <- "a4cea054-c92d-4764-970d-b3473239c939"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-raw-data-refresh", force = TRUE)
set_content_tags(content, tags$R$ETL)
set_image_path(content, "./content/01-etl/01-raw-data-refresh/icon.drawio.png")
```

#### 1.1.1 Pinned station info

Running the raw 1.1 Raw Data Refresh will update the following pin:

```{r}
# Pinned station info
guid <- "00036e13-9a3c-44c6-84eb-253de91b10c2"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_content_tags(content, tags$R$ETL)
set_image_path(content, "./img/icon-pins-data.drawio.png")
```

### 1.2 Tidy data

```{r}
guid <- "82fe2eea-0164-4823-98e3-ff15f1d31036"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-tidy-data", force = TRUE)
set_content_tags(content, tags$R$ETL)
set_image_path(content, "./content/01-etl/02-tidy-data/icon.drawio.png")
```

## 2 Model

### 2.1 Train and Deploy Model

```{r}
guid <- "07b3ff23-595b-4f8b-9f28-7c393cf230ef"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-train-and-deploy-model", force = TRUE)
set_content_tags(content, tags$R$Model)
set_image_path(content, "./content/02-model/01-train-and-deploy-model/icon.drawio.png")
```

#### 2.1.1 Pinned Model

Running the *2.1 Train and Deploy Model* script will update the following pinned model:

```{r}
# Pinned model
guid <- "0273207f-0f1f-44cb-845e-408f9dae2dd6"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_content_tags(content, tags$R$Model)
set_image_path(content, "./img/icon-pins-model.drawio.png")
```

#### 2.1.2 Deployed API

Running the *2.1 Train and Deploy Model* script will deplooy the following API:

```{r}
# Deployed API
guid <- "69186bcd-5a1d-4607-a68b-da78ee6cdf2a"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_content_tags(content, tags$R$Model)
set_image_path(content, "./img/icon-plumber.drawio.png")
```

### 2.2 Model Metrics

#### 2.2.1 Model Metrics Card

```{r}
guid <- "35a5a9c3-f8b1-414a-91cb-bdb5ad402580"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-model-metrics", force = TRUE)
set_content_tags(content, tags$R$Model)
set_image_path(content, "./content/02-model/02-model-metrics/icon.drawio.png")
```

#### 2.2.2 Model Metrics Pin

```{r}
guid <- "91d5bac2-db5f-44b6-b41b-d85138f48d8d"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-model-metrics-pin", force = TRUE)
set_content_tags(content, tags$R$Model)
set_image_path(content, "./img/icon-pins-model.drawio.png")
```


## 3 App

### 3.1 Client App

```{r}
guid <- "0477855b-caeb-43e8-b3d9-28e0965e6230"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-client-app", force = TRUE)
set_content_tags(content, tags$R$App)
set_image_path(content, "./content/03-app/01-client-app/icon.drawio.png")
```

### 3.2 Connect Widgets App

```{r}
guid <- "3124a8f9-7d30-44b9-a49a-552db71b036e"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-dashboard", force = TRUE)
set_content_tags(content, tags$R$App)
set_image_path(content, "./content/03-app/02-connect-widgets-app/icon.drawio.png")
```

### 3.3 Client App Dev

```{r}
guid <- "bdc0b532-6b42-4341-8310-73da49eafe09"
content <- content_item(client, guid)

# Configure content settings
content$update(access_type = "all")
set_vanity_url(content, "bike-predict-r-client-app-dev", force = TRUE)
set_content_tags(content, tags$R$App)
set_image_path(content, "./content/03-app/03-client-app-dev/icon.drawio.png")
```
