---
title: "Model - Model Card"
date: "`r lubridate::date(lubridate::now(tzone = 'EST'))`"
output: html_document
params:
    name: sam.edwardes/bike_predict_model_r
    version: NULL
---

```{r setup, include=FALSE}
library(tidyverse)
library(vetiver)
library(pins)
library(yardstick)
library(glue)

knitr::opts_chunk$set(echo = FALSE)

board <- pins::board_rsconnect()
v <- vetiver_pin_read(board, params$name, version = params$version)
v_meta <- pin_meta(board, params$name)
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

- Developed by Sam Edwardes (RStudio - Solutions Engineer)
- `r cli::pluralize("{v$description} using {ncol(v$ptype)} feature{?s}")`
- This model was developed to predict how many [capital bikeshare](https://capitalbikeshare.com) bikes will be available for a given station based on the time of day, and day of the week
- The data used to train the model was obtained from the [capital bikeshare API](https://ride.capitalbikeshare.com/system-data)
- Version `r v$metadata$version` of this model was published at `r v_meta$created`
- If you have questions about this model, please create an issue on our GitHub repo: <https://github.com/sol-eng/bike_predict/issues>

## Intended use

- The primary intended use of this model is to demonstrate an end-to-end data science workflow using [RStudio Connect](https://www.rstudio.com/products/connect/)

## Metrics

- The metrics used to evaluate this model are:
  - Root Mean Squared Error (RMSE)
  - R Squared (RSW)
  - Mean Absolute Error (MAE)
- We chose these metrics because because they are the most common metrics for assessing the performance of regression models, and that they are well understood by the data science community.

## Training data & evaluation data

```{r load_data}
con <- odbc::dbConnect(odbc::odbc(), "Content DB", timeout = 10)
bike_model_data <- tbl(con, "bike_model_data")


train_start_date <- lubridate::as_date(v$metadata$user$train_dates[1])
train_end_date <- lubridate::as_date(v$metadata$user$train_dates[2])
test_start_date <- lubridate::as_date(v$metadata$user$test_dates[1])
test_end_date <- lubridate::as_date(v$metadata$user$test_dates[2])

data <- bike_model_data %>%
  filter(date >= train_start_date) %>%
  collect() %>%
  mutate(
    data_type = case_when(
      date <= train_end_date ~ "train",
      date <= test_end_date ~ "test",
      TRUE ~ "latest"
    )
  )

train_data <- data %>%
  filter(data_type == "train")

test_data <- data %>%
  filter(data_type == "test")
```


::: {.panel-tabset}

### Overview

The training data set for this model was was obtained from the [capital bikeshare API](https://ride.capitalbikeshare.com/system-data). The Model is retrained on a daily basis using refreshed data.

- Training date range:  `r train_start_date` to `r train_end_date`.
- Evaluation date range: `r test_start_date` to `r test_end_date`.

The data set for this model has the "prototype" or signature:

```{r view_prototype}
glimpse(v$ptype)
```

### Training data

Below is a summary of the training data:

```{r skim_train_data}
train_data %>%
  select(-n_bikes) %>%
  skimr::skim()
```

### Evaluation data

Below is a summary of the evaluation data:

```{r skim_test_data}
test_data %>%
  select(-n_bikes) %>%
  skimr::skim()
```

:::

## Quantitative analyses 

::: {.panel-tabset}

```{r compute_preds, include=FALSE}
## compute predictions for your evaluation data
## `handler_startup` is designed to get the R process ready to make predictions
suppressPackageStartupMessages(handler_startup(v))

# Specifically load the packages required by the model. Check 
# `v$metadata$required_pkgs` to see the required packages. These packages must
# be specifically defined so that RStudio Connect knows to install them when
# deploying this document.
library(parsnip)
library(ranger)
library(recipes)
library(workflows)


preds <- augment(v, test_data)

latest_metrics <- preds %>%
  arrange(date) %>%
  vetiver_compute_metrics(
    date_var = date,
    period = "day",
    truth = n_bikes,
    estimate = .pred
  )
```

### Overall model performance

Overall model performance against the model evaluation data.

```{r view_latest_metrics}
# Explicitly define packages used for model metrics by vetiver so that Connect 
# is able to redeploy.
library(slider)

latest_metrics %>%
  kableExtra::kable()
```

### Visualize model performance

A comparison of the model prediction vs. the ground truth for the model evaluation data.

```{r preds_plot}
preds %>%
  ggplot(aes(n_bikes, .pred)) +
  geom_abline(slope = 1, lty = 2, color = "gray60", size = 1.2) +
  geom_jitter(alpha = 0.5, width = 0.4) +
  labs(
    title = glue("Model Performance on Evaluation Data ({test_start_date} to {test_end_date})"),
    x = "Acutal Number of Bikes",
    y = "Predicted Number of Bikes"
  )
```

### Performance by location

A visual assessment of model performance by location.

```{r preds_lat_lon_plot}
preds %>%
  mutate(.resid = n_bikes - .pred) %>%
  ggplot(aes(lon, lat, color = .resid)) +
  geom_point(alpha = 0.8) +
  scale_color_gradient2() +
  coord_fixed() + 
  labs(
    title = glue("Model Performance by Location on Evaluation Data ({test_start_date} to {test_end_date})"),
    x = "Longitude",
    y = "Latitude",
    color = "Redisual"
  )
```

:::

## Ethical considerations

- We considered the ethical impact the use of the model may have. We assessed that the overall risk an incorrect model prediction is relatively low.

## Caveats & recommendations

- This model does guarantee that a bike will be available at a station
- We recommend using this model for demonstration purposes only
- To see the raw source code that produced this document visit <https://github.com/sol-eng/bike_predict/blob/main/content/02-model/02-model-metrics/document.qmd>



