---
title: "Model Card: your model title"
date: '`r Sys.Date()`'
output: 
  html_document
params:
    board: !r pins::board_rsconnect()
    name: sam.edwardes/bike_predict_model_r
    version: NULL
---

```{r setup, include=FALSE}
library(tidyverse)
library(vetiver)
library(pins)
library(yardstick)
library(glue)
knitr::opts_chunk$set(echo = FALSE)
v <- vetiver_pin_read(params$board, params$name, version = params$version)
v_meta <- pin_meta(params$board, params$name)
theme_set(theme_light())
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

- Developed by PERSON AND/OR TEAM
- `r cli::pluralize("{v$description} using {ncol(v$ptype)} feature{?s}")`
- More details about how model was developed and what it is predicting
- More details on feature engineering and/or data preprocessing for model
- Version `r v$metadata$version` of this model was published at `r v_meta$created`
- Citation and/or license details for the model
- If you have questions about this model, please contact PERSON@ORG.ORG

## Intended use

- The primary intended uses of this model are ...
- The primary intended users of this model are ...
- Some use cases are out of scope for this model, such as ...

## Important aspects/factors

- Aspects or factors (demographic, environmental, technical) that are relevant to the context of this model are ...
- In evaluating this model, we examined aspects such as ...

## Metrics

- The metrics used to evaluate this model are ...
- These metrics are computed via ...
- We chose these metrics because ...

## Training data & evaluation data

```{r load_data}
con <- odbc::dbConnect(odbc::odbc(), "Content DB", timeout = 10)
bike_model_data <- tbl(con, "bike_model_data")

glue("Training dates: {paste(v$metadata$user$train_dates, collapse = ' to ')}")
glue("Testing dates:  {paste(v$metadata$user$test_dates, collapse = ' to ')}")

train_start_date <- lubridate::as_date(v$metadata$user$train_dates[1])
train_end_date <- lubridate::as_date(v$metadata$user$train_dates[2])
test_end_date <- lubridate::as_date(v$metadata$user$test_dates[2])

data <- bike_model_data %>%
  filter(date >= train_start_date) %>%
  collect() %>%
  mutate(
    data_type = case_when(
      date <= train_end_date ~ "train",
      date <= test_end_date ~ "test",
      TRUE ~ "latest"
    )
  )

train_data <- data %>%
  filter(data_type == "train")

test_data <- data %>%
  filter(data_type == "test")
```

- The training dataset for this model was ...

    ```{r}
    skimr::skim(train_data)
    ```

- The training dataset for this model has the "prototype" or signature:

    ```{r}
    glimpse(v$ptype)
    ```

- The evaluation dataset used in this model card is ...
- We chose this evaluation data because ...

```{r}
skimr::skim(test_data)
```


## Quantitative analyses {.tabset}

```{r}
## compute predictions for your evaluation data
## `handler_startup` is designed to get the R process ready to make predictions
suppressPackageStartupMessages(handler_startup(v))
preds <- augment(v, test_data)
```

### Overall model performance

```{r}
preds %>%
    metrics(n_bikes, .pred)
```

### Visualize model performance

```{r, fig.height=3}
preds %>%
    ggplot(aes(n_bikes, .pred)) +
    geom_abline(slope = 1, lty = 2, color = "gray60", size = 1.2) +
    geom_jitter(alpha = 0.5, show.legend = FALSE)
```

### Model performance by location

```{r}
preds %>%
    mutate(.resid = n_bikes - .pred) %>%
    ggplot(aes(lon, lat, color = .resid)) +
    geom_point(alpha = 0.8) +
    scale_color_gradient2() +
    coord_fixed()
```


## Ethical considerations

- We considered ...

## Caveats & recommendations

- This model does ...
- This model does not ...
- We recommend ...



